---
title: "Guidelines for Rmarkdown Documents in API-209/210 Submissions"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    template: memo_style.sty
    keep_tex: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      fig.width = 6, fig.height = 4, fig.align = "center")
```

## Output Format {-}

Output should be a PDF with the following regular formats:

- 11 or 12pt font
- reasonable margins (1 to 1.25 inches)
- a common font like Helvetica (this document), Times, or Computer Modern (Rmarkdown's default)
- A clear title which indicates your name, date, and problem set number

## Suppress code and warnings {-}

Because the point of most memos in a policy setting is not to show code, do not show the code that produces your output, unless to make a specific comment on the code. (This involves using the \code{echo = FALSE} to your code chunk as a default). To show your work, you'll be asked to submit your .Rmd file. 


Similarly, suppress output messages when loading packages (This can be done, for example, by using the \code{include = FALSE} option), and suppress warning or output messages for your code (this can be done, for example with the \code{warnings = FALSE`} option)



## Leveraging In-line R-code {-}

To avoid hard-coding answers, you are encouraged to write in-line R code in-text. For example, after assigning the number of rows of a dataset to an object, 

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
data(gss_cat)
n_gss <- nrow(gss_cat)
```

We can write in Rmarkdown 
\begin{quote}
\code{There are \textasciigrave r n\_gss\textasciigrave ~ observations in the GSS dataset.}
\end{quote}
which will produce the rendered text:


> There are `r format(n_gss, big.mark = ",")` observations in the GSS dataset.


## Use Section headers {-}

Label sections with headers using the \code{\#} symbol. 


## Templates {-}

Pre-made templates are useful for creating standardized documents. When using a PDF, you can provide a `.sty` file (written in TeX) in the same directoy as your `.Rmd` file and call it in the YAML header of your `.Rmd`, as in 

```{yaml, eval = FALSE}
---
title: "Guidelines for Rmarkdown Documents in API-209/210 Submissions"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  pdf_document:
    template: pset_style.sty
---
```

where `ps_style.sty` is the style file. A style file you are welcome to use is uploaded [at this link](https://github.com/kuriwaki/rmd-template/blob/master/pset_style.sty) -- click "Raw" to copy the contents of this file.