---
title: "Guidlines for R Markdown Documents in API-209/210 Submissions"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    word_document:
        reference_docx: template.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      fig.width = 6, fig.height = 4, fig.align = "center")
```

R Markdown is a poweful tool for data analysis and presentation. A modal R Markdown document combines three different languages: R, Markdown, and TeX (and implicitly a fourth, called Pandoc), so we advise using R Markdown once you are comfortable in at least one of these formats. 

The RStudio IDE makes it easy to create and compile R Markdown documents. You can start by `File` > `New File` > `R Markdown`, and choosing to output as PDF with the default options. [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/) is also available for online. The teaching team will spend time making sure everyone can has a basic command of R Markdown, as we prepare for API-210. In API-209, the use of R Markdown is completely optional. 

R Markdown documents can be customized, and because this is a problem set we ask you to follow the guidelines below. Otherwise, it will be hard for the teaching team to grade and compare a high volume of submissions in a timely manner. Please refer to these below and contact Shiro if you'd like any help or guidance. 


## Output Format {-}

Problem Set submissions should be a PDF with the following basic features:

- 11 or 12pt-sized font
- Reasonable margins (1 to 1.25 inches)
- Use a common font like Helvetica, Times, or Computer Modern (Rmarkdown's default)
- Include a clear title which indicates your name, date, and problem set number

## Suppress code and warnings {-}

Because the point of most policy memos is not to show code, do _not_ show the code that produces your output, unless to make a specific comment on the code. This involves using the \code{echo = FALSE} to your code chunk as a default.^[To show your work, you'll be asked to submit your .Rmd file separately.] 


Similarly, suppress output messages when loading packages (This can be done, for example, by using the \code{include = FALSE} option), and suppress warning or output messages for your code (this can be done, for example with the \code{warnings = FALSE`} option)


## Leveraging In-line R-code {-}

To avoid hard-coding answers, you are encouraged to write in-line R code in-text. For example, after assigning the number of rows of a dataset to an object, 

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
data(gss_cat)
n_gss <- nrow(gss_cat)
```

We can write in Rmarkdown 
\begin{quote}
\code{There are \textasciigrave r n\_gss\textasciigrave ~ observations in the GSS dataset.}
\end{quote}
which will produce the  text:

> There are `r n_gss` observations in the GSS dataset.

Any line of R code can go in the back-ticks. As a simple extension, 

\begin{quote}
\code{There are \textasciigrave r format(n\_gss, big.mark = ",")\textasciigrave observations.}
\end{quote}
will produce the output produced by the R function:

> There are `r format(n_gss, big.mark = ",")` observations.

## Use Section headers {-}

Label sections with headers using the \code{\#} symbol. Another useful section delimiter in PDF is the paragraph header command, which you can use by, for example, `\paragraph{(1)}`


## Templates {-}

Pre-made templates are useful for creating standardized documents. When using a PDF, you can provide a `.sty` file (a file format for documents written in TeX) in the same directory as your `.Rmd` file and call it in the YAML header of your `.Rmd`, as in 

```{yaml, eval = FALSE}
---
title: "Problem Set 10"
author: "Shiro Kuriwaki"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  pdf_document:
    template: pset.sty
---
```

where `pset.sty` is the style file. A style file you are welcome to use is uploaded [at this link](https://github.com/kuriwaki/rmd-template/blob/master/pset.sty) -- click "Raw" to copy the contents of this file.